---
title: "edinetsynth: Quick Start Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{edinetsynth: Quick Start Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 10,
  fig.height = 6,
  out.width = "100%"
)
```

## What is edinetsynth?

`edinetsynth` is the companion R package for VilseckKI synthetic EDINET datasets
-- quality-tiered Japanese securities reports (有価証券報告書) with verified
FSA compliance flaws.

This vignette demonstrates the full evaluation pipeline using built-in sample
data. No external files needed.

## Step 1: Generate sample data

```{r load}
library(edinetsynth)

# Built-in sample data generator (50 documents, 4 quality tiers)
reports <- make_sample_data(n = 50)
cat("Documents:", nrow(reports), "\n")
cat("Columns:", paste(names(reports), collapse = ", "), "\n")
```

## Step 2: Inspect segment statistics

Each document has 8 sections matching real 有価証券報告書 structure.

```{r segments}
stats <- segment_summary(reports)
print(stats)
```

## Step 3: Check quality tier distribution

The dataset uses a 4-tier system: perfect (80%), near (10%), moderate (8%),
severe (2%). Higher tiers contain progressively more FSA compliance flaws.

```{r tiers}
tiers <- compare_tiers(reports)
print(tiers)
```

## Step 4: Detect flaws

`detect_flaws()` runs heuristic anomaly detectors. In a real dataset, flaws
are *planted deliberately* in Tier 2-4 documents and verified via triangulated
QA (keyword detection + LLM blind extraction).

```{r flaws}
flaws <- detect_flaws(reports)
cat("Total flaws detected:", nrow(flaws), "\n")
if (nrow(flaws) > 0) {
  print(table(flaws$flaw_type, flaws$severity))
}
```

## Step 5: Extract segments for NLP

Feed individual sections directly into your tokenizer or fine-tuning pipeline.

```{r extract}
risks <- extract_segment(reports, "business_risks", with_id = TRUE)
cat("Non-empty risk sections:", sum(nchar(as.character(risks[[2]])) > 0),
    "/", nrow(risks), "\n")
```

## Step 6: Generate marketplace visualizations

```{r plots, eval = FALSE}
# Generates PNG files in the specified directory
plot_quality_report(reports, output_dir = "eval_plots/")
plot_advanced_quality(reports, output_dir = "eval_plots/")

# The "money shot" -- FSA verification summary (uses sample data)
plot_fsa_verification_summary(output_path = "eval_plots/fsa_summary.png")
```

## Step 7: Export to HuggingFace format

```{r export, eval = FALSE}
export_to_hf_dataset(
  reports,
  output_dir = "hf_export/",
  stratify_by = "quality_tier"
)
# Produces: train.jsonl, test.jsonl, dataset_info.json
# Load in Python: datasets.load_dataset("json", data_files={...})
```

## Step 8: Experiment with anomaly injection

`inject_anomalies()` lets you create additional training scenarios
by programmatically introducing flaws into clean documents.

```{r inject}
augmented <- inject_anomalies(reports, flaw_type = "generic_language", rate = 0.1)
cat("Documents with injected flaws:",
    sum(!is.na(augmented$injected_flaw)), "\n")
```

## Citation

```{r citation, eval = FALSE}
edinetsynth_citation()
```

For more information, visit the
[JDEX listing](https://jdex.jp) (search: VilseckKI)
or the [GitHub repository](https://github.com/misawa-data-gk/edinetsynth).
